Evaluating Class Imbalance

### 2019-05-08 Scripts/evaluating_imbalance_ratios.Rmd
editted results script

```{r}
train <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/train.rds")
test <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/test.rds")

set.seed(123)
sampids <- sample(which(train$y=="No"),
                        length(which(train$y=="Yes")),
                        replace = FALSE)
data.rus <- rbind.data.frame(train[which(train$y=="Yes"),],
                           train[sampids,])

set.seed(123)		
sampids <- sample(which(train$y=="Yes"),
                        length(which(train$y=="No")),
                        replace = TRUE)
data.ros <- rbind.data.frame(train[which(train$y=="No"),],
                           train[sampids,])

set.seed(123)
data.sm <- SMOTE(y ~ ., 
                     data=train, 
                     perc.over = 100, 
                     perc.under = 200)

names(train)[-1] <- gsub("-","_",names(train)[-1])
data.rose <- ROSE(y ~ ., data=train,seed=1,p=0.5)$data

#set.seed(123)
#n <- 1000
#nr <- nrow(train)
#splitdat <- split(train, rep(1:ceiling(nr/n), each=n, length.out=nr))
#meds <- max(unlist(lapply(splitdat, function(x){length(which(x$y=="Yes"))})))
#medoids <- list(as.numeric(),length(splitdat))
#for(i in 1:length(splitdat)){
#  print(i)
#  data <- splitdat[[i]]
#  majority <- data[which(data$y=="No"),-1]
#  minnum <- length(which(data$y=="Yes"))
# 
#  pam.med <- pam(majority, k = minnum, diss = FALSE,
#                 metric = "manhattan", 
#                 #medoids = NULL, 
#                 #stand = FALSE, 
#                 cluster.only = FALSE,
#                 do.swap = TRUE,
#                 keep.diss = FALSE,
#                 keep.data = FALSE,
#                 pamonce = FALSE, trace.lev = 2)
#  
#  medoids[[i]] <- as.numeric(rownames(pam.med$medoids))
#  
#}
#medoids <- unlist(medoids)
#data.km <- rbind.data.frame(train[which(as.numeric(rownames(train)) %in% medoids),],
#                               train[which(train$y=="Yes"),])

x10 <- data.frame(IR = c((length(train$y[which(train$y=="Yes")])+length(test$y[which(test$y=="Yes")]))/(length(train$y[which(train$y=="No")])+length(test$y[which(test$y=="No")])), 
					  length(train$y[which(train$y=="Yes")])/length(train$y[which(train$y=="No")]),
					  length(test$y[which(test$y=="Yes")])/length(test$y[which(test$y=="No")]),
					  length(data.rus$y[which(data.rus$y=="Yes")])/length(data.rus$y[which(data.rus$y=="No")]),
					  length(data.ros$y[which(data.ros$y=="Yes")])/length(data.ros$y[which(data.ros$y=="No")]),
					  length(data.sm$y[which(data.sm$y=="Yes")])/length(data.sm$y[which(data.sm$y=="No")]),
					  length(data.rose$y[which(data.rose$y=="Yes")])/length(data.rose$y[which(data.rose$y=="No")])),
					  #length(data.km$y[which(data.km$y=="No")]), 
					  #length(data.km$y[which(data.km$y=="Yes")])),
			    CB = c("Complete",
					   "Train",
					   "Test",
					   "Under-Sampling",
					   "Over-Sampling",
					   "SMOTE",
					   "ROSE"))

p10kb <- ggplot(x10, aes(y=IR, x=factor(CB, levels = unique(x10$CB)))) + 
  geom_bar( stat="identity") +
  ylab("Imbalance Ratio")+
  xlab("")+
  #ylim(0, 30000)+
  theme_bw() +
  #guides(fill=FALSE)+
  theme(axis.text.x = element_text(size=15, 
                                   angle = 45, 
                                   #margin = ggplot2::margin(t = 35),
                                   hjust = 1),
        axis.text.y = element_text(size = 15),
        #axis.title.x = element_text(size = 15),
        axis.title.y = element_text(size = 15))

@@

```{r}
train <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/training_testing/train.rds")
test <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/training_testing/test.rds")

set.seed(123)
sampids <- sample(which(train$y=="No"),
                        length(which(train$y=="Yes")),
                        replace = FALSE)
data.rus <- rbind.data.frame(train[which(train$y=="Yes"),],
                           train[sampids,])

set.seed(123)		
sampids <- sample(which(train$y=="Yes"),
                        length(which(train$y=="No")),
                        replace = TRUE)
data.ros <- rbind.data.frame(train[which(train$y=="No"),],
                           train[sampids,])

set.seed(123)
data.sm <- SMOTE(y ~ ., 
                     data=train, 
                     perc.over = 100, 
                     perc.under = 200)

names(train)[-1] <- gsub("-","_",names(train)[-1])
data.rose <- ROSE(y ~ ., data=train,seed=1,p=0.5)$data

#set.seed(123)
#n <- 1000
#nr <- nrow(train)
#splitdat <- split(train, rep(1:ceiling(nr/n), each=n, length.out=nr))
#meds <- max(unlist(lapply(splitdat, function(x){length(which(x$y=="Yes"))})))
#medoids <- list(as.numeric(),length(splitdat))
#for(i in 1:length(splitdat)){
#  print(i)
#  data <- splitdat[[i]]
#  majority <- data[which(data$y=="No"),-1]
#  minnum <- length(which(data$y=="Yes"))
# 
#  pam.med <- pam(majority, k = minnum, diss = FALSE,
#                 metric = "manhattan", 
#                 #medoids = NULL, 
#                 #stand = FALSE, 
#                 cluster.only = FALSE,
#                 do.swap = TRUE,
#                 keep.diss = FALSE,
#                 keep.data = FALSE,
#                 pamonce = FALSE, trace.lev = 2)
#  
#  medoids[[i]] <- as.numeric(rownames(pam.med$medoids))
#  
#}
#medoids <- unlist(medoids)
#data.km <- rbind.data.frame(train[which(as.numeric(rownames(train)) %in% medoids),],
#                               train[which(train$y=="Yes"),])

x25 <- data.frame(IR = c((length(train$y[which(train$y=="Yes")])+length(test$y[which(test$y=="Yes")]))/(length(train$y[which(train$y=="No")])+length(test$y[which(test$y=="No")])), 
					  length(train$y[which(train$y=="Yes")])/length(train$y[which(train$y=="No")]),
					  length(test$y[which(test$y=="Yes")])/length(test$y[which(test$y=="No")]),
					  length(data.rus$y[which(data.rus$y=="Yes")])/length(data.rus$y[which(data.rus$y=="No")]),
					  length(data.ros$y[which(data.ros$y=="Yes")])/length(data.ros$y[which(data.ros$y=="No")]),
					  length(data.sm$y[which(data.sm$y=="Yes")])/length(data.sm$y[which(data.sm$y=="No")]),
					  length(data.rose$y[which(data.rose$y=="Yes")])/length(data.rose$y[which(data.rose$y=="No")])),
					  #length(data.km$y[which(data.km$y=="No")]), 
					  #length(data.km$y[which(data.km$y=="Yes")])),
			    CB = c("Complete",
					   "Train",
					   "Test",
					   "Under-Sampling",
					   "Over-Sampling",
					   "SMOTE",
					   "ROSE"))

p25kb <- ggplot(x25, aes(y=IR, x=factor(CB, levels = unique(x25$CB)))) + 
  geom_bar( stat="identity") +
  ylab("Imbalance Ratio")+
  xlab("")+
  #ylim(0, 30000)+
  theme_bw() +
  #guides(fill=FALSE)+
  theme(axis.text.x = element_text(size=15, 
                                   angle = 45, 
                                   #margin = ggplot2::margin(t = 35),
                                   hjust = 1),
        axis.text.y = element_text(size = 15),
        #axis.title.x = element_text(size = 15),
        axis.title.y = element_text(size = 15))

@@

```{r}
train <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/training_testing/train.rds")
test <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/training_testing/test.rds")

set.seed(123)
sampids <- sample(which(train$y=="No"),
                        length(which(train$y=="Yes")),
                        replace = FALSE)
data.rus <- rbind.data.frame(train[which(train$y=="Yes"),],
                           train[sampids,])

set.seed(123)		
sampids <- sample(which(train$y=="Yes"),
                        length(which(train$y=="No")),
                        replace = TRUE)
data.ros <- rbind.data.frame(train[which(train$y=="No"),],
                           train[sampids,])

set.seed(123)
data.sm <- SMOTE(y ~ ., 
                     data=train, 
                     perc.over = 100, 
                     perc.under = 200)

names(train)[-1] <- gsub("-","_",names(train)[-1])
data.rose <- ROSE(y ~ ., data=train,seed=1,p=0.5)$data

#set.seed(123)
#n <- 1000
#nr <- nrow(train)
#splitdat <- split(train, rep(1:ceiling(nr/n), each=n, length.out=nr))
#meds <- max(unlist(lapply(splitdat, function(x){length(which(x$y=="Yes"))})))
#medoids <- list(as.numeric(),length(splitdat))
#for(i in 1:length(splitdat)){
#  print(i)
#  data <- splitdat[[i]]
#  majority <- data[which(data$y=="No"),-1]
#  minnum <- length(which(data$y=="Yes"))
# 
#  pam.med <- pam(majority, k = minnum, diss = FALSE,
#                 metric = "manhattan", 
#                 #medoids = NULL, 
#                 #stand = FALSE, 
#                 cluster.only = FALSE,
#                 do.swap = TRUE,
#                 keep.diss = FALSE,
#                 keep.data = FALSE,
#                 pamonce = FALSE, trace.lev = 2)
#  
#  medoids[[i]] <- as.numeric(rownames(pam.med$medoids))
#  
#}
#medoids <- unlist(medoids)
#data.km <- rbind.data.frame(train[which(as.numeric(rownames(train)) %in% medoids),],
#                               train[which(train$y=="Yes"),])

x50 <- data.frame(IR = c((length(train$y[which(train$y=="Yes")])+length(test$y[which(test$y=="Yes")]))/(length(train$y[which(train$y=="No")])+length(test$y[which(test$y=="No")])), 
					  length(train$y[which(train$y=="Yes")])/length(train$y[which(train$y=="No")]),
					  length(test$y[which(test$y=="Yes")])/length(test$y[which(test$y=="No")]),
					  length(data.rus$y[which(data.rus$y=="Yes")])/length(data.rus$y[which(data.rus$y=="No")]),
					  length(data.ros$y[which(data.ros$y=="Yes")])/length(data.ros$y[which(data.ros$y=="No")]),
					  length(data.sm$y[which(data.sm$y=="Yes")])/length(data.sm$y[which(data.sm$y=="No")]),
					  length(data.rose$y[which(data.rose$y=="Yes")])/length(data.rose$y[which(data.rose$y=="No")])),
					  #length(data.km$y[which(data.km$y=="No")]), 
					  #length(data.km$y[which(data.km$y=="Yes")])),
			    CB = c("Complete",
					   "Train",
					   "Test",
					   "Under-Sampling",
					   "Over-Sampling",
					   "SMOTE",
					   "ROSE"))

p50kb <- ggplot(x50, aes(y=IR, x=factor(CB, levels = unique(x50$CB)))) + 
  geom_bar( stat="identity") +
  ylab("Imbalance Ratio")+
  xlab("")+
  #ylim(0, 30000)+
  theme_bw() +
  #guides(fill=FALSE)+
  theme(axis.text.x = element_text(size=15, 
                                   angle = 45, 
                                   #margin = ggplot2::margin(t = 35),
                                   hjust = 1),
        axis.text.y = element_text(size = 15),
        #axis.title.x = element_text(size = 15),
        axis.title.y = element_text(size = 15))

@@

```{r}
train <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/training_testing/train.rds")
test <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/training_testing/test.rds")

set.seed(123)
sampids <- sample(which(train$y=="No"),
                        length(which(train$y=="Yes")),
                        replace = FALSE)
data.rus <- rbind.data.frame(train[which(train$y=="Yes"),],
                           train[sampids,])

set.seed(123)		
sampids <- sample(which(train$y=="Yes"),
                        length(which(train$y=="No")),
                        replace = TRUE)
data.ros <- rbind.data.frame(train[which(train$y=="No"),],
                           train[sampids,])

set.seed(123)
data.sm <- SMOTE(y ~ ., 
                     data=train, 
                     perc.over = 100, 
                     perc.under = 200)

names(train)[-1] <- gsub("-","_",names(train)[-1])
data.rose <- ROSE(y ~ ., data=train,seed=1,p=0.5)$data

#set.seed(123)
#n <- 1000
#nr <- nrow(train)
#splitdat <- split(train, rep(1:ceiling(nr/n), each=n, length.out=nr))
#meds <- max(unlist(lapply(splitdat, function(x){length(which(x$y=="Yes"))})))
#medoids <- list(as.numeric(),length(splitdat))
#for(i in 1:length(splitdat)){
#  print(i)
#  data <- splitdat[[i]]
#  majority <- data[which(data$y=="No"),-1]
#  minnum <- length(which(data$y=="Yes"))
# 
#  pam.med <- pam(majority, k = minnum, diss = FALSE,
#                 metric = "manhattan", 
#                 #medoids = NULL, 
#                 #stand = FALSE, 
#                 cluster.only = FALSE,
#                 do.swap = TRUE,
#                 keep.diss = FALSE,
#                 keep.data = FALSE,
#                 pamonce = FALSE, trace.lev = 2)
#  
#  medoids[[i]] <- as.numeric(rownames(pam.med$medoids))
#  
#}
#medoids <- unlist(medoids)
#data.km <- rbind.data.frame(train[which(as.numeric(rownames(train)) %in% medoids),],
#                               train[which(train$y=="Yes"),])

x100 <- data.frame(IR = c((length(train$y[which(train$y=="Yes")])+length(test$y[which(test$y=="Yes")]))/(length(train$y[which(train$y=="No")])+length(test$y[which(test$y=="No")])), 
					  length(train$y[which(train$y=="Yes")])/length(train$y[which(train$y=="No")]),
					  length(test$y[which(test$y=="Yes")])/length(test$y[which(test$y=="No")]),
					  length(data.rus$y[which(data.rus$y=="Yes")])/length(data.rus$y[which(data.rus$y=="No")]),
					  length(data.ros$y[which(data.ros$y=="Yes")])/length(data.ros$y[which(data.ros$y=="No")]),
					  length(data.sm$y[which(data.sm$y=="Yes")])/length(data.sm$y[which(data.sm$y=="No")]),
					  length(data.rose$y[which(data.rose$y=="Yes")])/length(data.rose$y[which(data.rose$y=="No")])),
					  #length(data.km$y[which(data.km$y=="No")]), 
					  #length(data.km$y[which(data.km$y=="Yes")])),
			    CB = c("Complete",
					   "Train",
					   "Test",
					   "Under-Sampling",
					   "Over-Sampling",
					   "SMOTE",
					   "ROSE"))

p100kb <- ggplot(x100, aes(y=IR, x=factor(CB, levels = unique(x100$CB)))) + 
  geom_bar( stat="identity") +
  ylab("Imbalance Ratio")+
  xlab("")+
  #ylim(0, 30000)+
  theme_bw() +
  #guides(fill=FALSE)+
  theme(axis.text.x = element_text(size=15, 
                                   angle = 45, 
                                   #margin = ggplot2::margin(t = 35),
                                   hjust = 1),
        axis.text.y = element_text(size = 15),
        #axis.title.x = element_text(size = 15),
        axis.title.y = element_text(size = 15))

@@

```{r}
train <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/train.rds")
test <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/test.rds")

set.seed(123)
sampids <- sample(which(train$y=="No"),
                        length(which(train$y=="Yes")),
                        replace = FALSE)
data.rus <- rbind.data.frame(train[which(train$y=="Yes"),],
                           train[sampids,])

set.seed(123)		
sampids <- sample(which(train$y=="Yes"),
                        length(which(train$y=="No")),
                        replace = TRUE)
data.ros <- rbind.data.frame(train[which(train$y=="No"),],
                           train[sampids,])

set.seed(123)
data.sm <- SMOTE(y ~ ., 
                     data=train, 
                     perc.over = 100, 
                     perc.under = 200)

names(train)[-1] <- gsub("-","_",names(train)[-1])
data.rose <- ROSE(y ~ ., data=train,seed=1,p=0.5)$data

#set.seed(123)
#n <- 1000
#nr <- nrow(train)
#splitdat <- split(train, rep(1:ceiling(nr/n), each=n, length.out=nr))
#meds <- max(unlist(lapply(splitdat, function(x){length(which(x$y=="Yes"))})))
#medoids <- list(as.numeric(),length(splitdat))
#for(i in 1:length(splitdat)){
#  print(i)
#  data <- splitdat[[i]]
#  majority <- data[which(data$y=="No"),-1]
#  minnum <- length(which(data$y=="Yes"))
# 
#  pam.med <- pam(majority, k = minnum, diss = FALSE,
#                 metric = "manhattan", 
#                 #medoids = NULL, 
#                 #stand = FALSE, 
#                 cluster.only = FALSE,
#                 do.swap = TRUE,
#                 keep.diss = FALSE,
#                 keep.data = FALSE,
#                 pamonce = FALSE, trace.lev = 2)
#  
#  medoids[[i]] <- as.numeric(rownames(pam.med$medoids))
#  
#}
#medoids <- unlist(medoids)
#data.km <- rbind.data.frame(train[which(as.numeric(rownames(train)) %in% medoids),],
#                               train[which(train$y=="Yes"),])

x10_k562 <- data.frame(IR = c((length(train$y[which(train$y=="Yes")])+length(test$y[which(test$y=="Yes")]))/(length(train$y[which(train$y=="No")])+length(test$y[which(test$y=="No")])), 
					  length(train$y[which(train$y=="Yes")])/length(train$y[which(train$y=="No")]),
					  length(test$y[which(test$y=="Yes")])/length(test$y[which(test$y=="No")]),
					  length(data.rus$y[which(data.rus$y=="Yes")])/length(data.rus$y[which(data.rus$y=="No")]),
					  length(data.ros$y[which(data.ros$y=="Yes")])/length(data.ros$y[which(data.ros$y=="No")]),
					  length(data.sm$y[which(data.sm$y=="Yes")])/length(data.sm$y[which(data.sm$y=="No")]),
					  length(data.rose$y[which(data.rose$y=="Yes")])/length(data.rose$y[which(data.rose$y=="No")])),
					  #length(data.km$y[which(data.km$y=="No")]), 
					  #length(data.km$y[which(data.km$y=="Yes")])),
			    CB = c("Complete",
					   "Train",
					   "Test",
					   "Under-Sampling",
					   "Over-Sampling",
					   "SMOTE",
					   "ROSE"))

p10kb_k562 <- ggplot(x10_k562, aes(y=IR, x=factor(CB, levels = unique(x10_k562$CB)))) + 
  geom_bar( stat="identity") +
  ylab("Imbalance Ratio")+
  xlab("")+
  #ylim(0, 30000)+
  theme_bw() +
  #guides(fill=FALSE)+
  theme(axis.text.x = element_text(size=15, 
                                   angle = 45, 
                                   #margin = ggplot2::margin(t = 35),
                                   hjust = 1),
        axis.text.y = element_text(size = 15),
        #axis.title.x = element_text(size = 15),
        axis.title.y = element_text(size = 15))

@@

```{r}
train <- readRDS("Z:/TAD_data_analysis/K562/25kb/training_testing/train.rds")
test <- readRDS("Z:/TAD_data_analysis/K562/25kb/training_testing/test.rds")

set.seed(123)
sampids <- sample(which(train$y=="No"),
                        length(which(train$y=="Yes")),
                        replace = FALSE)
data.rus <- rbind.data.frame(train[which(train$y=="Yes"),],
                           train[sampids,])

set.seed(123)		
sampids <- sample(which(train$y=="Yes"),
                        length(which(train$y=="No")),
                        replace = TRUE)
data.ros <- rbind.data.frame(train[which(train$y=="No"),],
                           train[sampids,])

set.seed(123)
data.sm <- SMOTE(y ~ ., 
                     data=train, 
                     perc.over = 100, 
                     perc.under = 200)

names(train)[-1] <- gsub("-","_",names(train)[-1])
data.rose <- ROSE(y ~ ., data=train,seed=1,p=0.5)$data

#set.seed(123)
#n <- 1000
#nr <- nrow(train)
#splitdat <- split(train, rep(1:ceiling(nr/n), each=n, length.out=nr))
#meds <- max(unlist(lapply(splitdat, function(x){length(which(x$y=="Yes"))})))
#medoids <- list(as.numeric(),length(splitdat))
#for(i in 1:length(splitdat)){
#  print(i)
#  data <- splitdat[[i]]
#  majority <- data[which(data$y=="No"),-1]
#  minnum <- length(which(data$y=="Yes"))
# 
#  pam.med <- pam(majority, k = minnum, diss = FALSE,
#                 metric = "manhattan", 
#                 #medoids = NULL, 
#                 #stand = FALSE, 
#                 cluster.only = FALSE,
#                 do.swap = TRUE,
#                 keep.diss = FALSE,
#                 keep.data = FALSE,
#                 pamonce = FALSE, trace.lev = 2)
#  
#  medoids[[i]] <- as.numeric(rownames(pam.med$medoids))
#  
#}
#medoids <- unlist(medoids)
#data.km <- rbind.data.frame(train[which(as.numeric(rownames(train)) %in% medoids),],
#                               train[which(train$y=="Yes"),])

x25_k562 <- data.frame(IR = c((length(train$y[which(train$y=="Yes")])+length(test$y[which(test$y=="Yes")]))/(length(train$y[which(train$y=="No")])+length(test$y[which(test$y=="No")])), 
					  length(train$y[which(train$y=="Yes")])/length(train$y[which(train$y=="No")]),
					  length(test$y[which(test$y=="Yes")])/length(test$y[which(test$y=="No")]),
					  length(data.rus$y[which(data.rus$y=="Yes")])/length(data.rus$y[which(data.rus$y=="No")]),
					  length(data.ros$y[which(data.ros$y=="Yes")])/length(data.ros$y[which(data.ros$y=="No")]),
					  length(data.sm$y[which(data.sm$y=="Yes")])/length(data.sm$y[which(data.sm$y=="No")]),
					  length(data.rose$y[which(data.rose$y=="Yes")])/length(data.rose$y[which(data.rose$y=="No")])),
					  #length(data.km$y[which(data.km$y=="No")]), 
					  #length(data.km$y[which(data.km$y=="Yes")])),
			    CB = c("Complete",
					   "Train",
					   "Test",
					   "Under-Sampling",
					   "Over-Sampling",
					   "SMOTE",
					   "ROSE"))

p25kb_k562 <- ggplot(x25_k562, aes(y=IR, x=factor(CB, levels = unique(x25_k562$CB)))) + 
  geom_bar( stat="identity") +
  ylab("Imbalance Ratio")+
  xlab("")+
  #ylim(0, 30000)+
  theme_bw() +
  #guides(fill=FALSE)+
  theme(axis.text.x = element_text(size=15, 
                                   angle = 45, 
                                   #margin = ggplot2::margin(t = 35),
                                   hjust = 1),
        axis.text.y = element_text(size = 15),
        #axis.title.x = element_text(size = 15),
        axis.title.y = element_text(size = 15))

@@

```{r}
train <- readRDS("Z:/TAD_data_analysis/K562/50kb/training_testing/train.rds")
test <- readRDS("Z:/TAD_data_analysis/K562/50kb/training_testing/test.rds")

set.seed(123)
sampids <- sample(which(train$y=="No"),
                        length(which(train$y=="Yes")),
                        replace = FALSE)
data.rus <- rbind.data.frame(train[which(train$y=="Yes"),],
                           train[sampids,])

set.seed(123)		
sampids <- sample(which(train$y=="Yes"),
                        length(which(train$y=="No")),
                        replace = TRUE)
data.ros <- rbind.data.frame(train[which(train$y=="No"),],
                           train[sampids,])

set.seed(123)
data.sm <- SMOTE(y ~ ., 
                     data=train, 
                     perc.over = 100, 
                     perc.under = 200)

names(train)[-1] <- gsub("-","_",names(train)[-1])
data.rose <- ROSE(y ~ ., data=train,seed=1,p=0.5)$data

#set.seed(123)
#n <- 1000
#nr <- nrow(train)
#splitdat <- split(train, rep(1:ceiling(nr/n), each=n, length.out=nr))
#meds <- max(unlist(lapply(splitdat, function(x){length(which(x$y=="Yes"))})))
#medoids <- list(as.numeric(),length(splitdat))
#for(i in 1:length(splitdat)){
#  print(i)
#  data <- splitdat[[i]]
#  majority <- data[which(data$y=="No"),-1]
#  minnum <- length(which(data$y=="Yes"))
# 
#  pam.med <- pam(majority, k = minnum, diss = FALSE,
#                 metric = "manhattan", 
#                 #medoids = NULL, 
#                 #stand = FALSE, 
#                 cluster.only = FALSE,
#                 do.swap = TRUE,
#                 keep.diss = FALSE,
#                 keep.data = FALSE,
#                 pamonce = FALSE, trace.lev = 2)
#  
#  medoids[[i]] <- as.numeric(rownames(pam.med$medoids))
#  
#}
#medoids <- unlist(medoids)
#data.km <- rbind.data.frame(train[which(as.numeric(rownames(train)) %in% medoids),],
#                               train[which(train$y=="Yes"),])

x50_k562 <- data.frame(IR = c((length(train$y[which(train$y=="Yes")])+length(test$y[which(test$y=="Yes")]))/(length(train$y[which(train$y=="No")])+length(test$y[which(test$y=="No")])), 
					  length(train$y[which(train$y=="Yes")])/length(train$y[which(train$y=="No")]),
					  length(test$y[which(test$y=="Yes")])/length(test$y[which(test$y=="No")]),
					  length(data.rus$y[which(data.rus$y=="Yes")])/length(data.rus$y[which(data.rus$y=="No")]),
					  length(data.ros$y[which(data.ros$y=="Yes")])/length(data.ros$y[which(data.ros$y=="No")]),
					  length(data.sm$y[which(data.sm$y=="Yes")])/length(data.sm$y[which(data.sm$y=="No")]),
					  length(data.rose$y[which(data.rose$y=="Yes")])/length(data.rose$y[which(data.rose$y=="No")])),
					  #length(data.km$y[which(data.km$y=="No")]), 
					  #length(data.km$y[which(data.km$y=="Yes")])),
			    CB = c("Complete",
					   "Train",
					   "Test",
					   "Under-Sampling",
					   "Over-Sampling",
					   "SMOTE",
					   "ROSE"))

p50kb_k562 <- ggplot(x50_k562, aes(y=IR, x=factor(CB, levels = unique(x50_k562$CB)))) + 
  geom_bar( stat="identity") +
  ylab("Imbalance Ratio")+
  xlab("")+
  #ylim(0, 30000)+
  theme_bw() +
  #guides(fill=FALSE)+
  theme(axis.text.x = element_text(size=15, 
                                   angle = 45, 
                                   #margin = ggplot2::margin(t = 35),
                                   hjust = 1),
        axis.text.y = element_text(size = 15),
        #axis.title.x = element_text(size = 15),
        axis.title.y = element_text(size = 15))

@@

```{r}
train <- readRDS("Z:/TAD_data_analysis/K562/100kb/training_testing/train.rds")
test <- readRDS("Z:/TAD_data_analysis/K562/100kb/training_testing/test.rds")

set.seed(123)
sampids <- sample(which(train$y=="No"),
                        length(which(train$y=="Yes")),
                        replace = FALSE)
data.rus <- rbind.data.frame(train[which(train$y=="Yes"),],
                           train[sampids,])

set.seed(123)		
sampids <- sample(which(train$y=="Yes"),
                        length(which(train$y=="No")),
                        replace = TRUE)
data.ros <- rbind.data.frame(train[which(train$y=="No"),],
                           train[sampids,])

set.seed(123)
data.sm <- SMOTE(y ~ ., 
                     data=train, 
                     perc.over = 100, 
                     perc.under = 200)

names(train)[-1] <- gsub("-","_",names(train)[-1])
data.rose <- ROSE(y ~ ., data=train,seed=1,p=0.5)$data

#set.seed(123)
#n <- 1000
#nr <- nrow(train)
#splitdat <- split(train, rep(1:ceiling(nr/n), each=n, length.out=nr))
#meds <- max(unlist(lapply(splitdat, function(x){length(which(x$y=="Yes"))})))
#medoids <- list(as.numeric(),length(splitdat))
#for(i in 1:length(splitdat)){
#  print(i)
#  data <- splitdat[[i]]
#  majority <- data[which(data$y=="No"),-1]
#  minnum <- length(which(data$y=="Yes"))
# 
#  pam.med <- pam(majority, k = minnum, diss = FALSE,
#                 metric = "manhattan", 
#                 #medoids = NULL, 
#                 #stand = FALSE, 
#                 cluster.only = FALSE,
#                 do.swap = TRUE,
#                 keep.diss = FALSE,
#                 keep.data = FALSE,
#                 pamonce = FALSE, trace.lev = 2)
#  
#  medoids[[i]] <- as.numeric(rownames(pam.med$medoids))
#  
#}
#medoids <- unlist(medoids)
#data.km <- rbind.data.frame(train[which(as.numeric(rownames(train)) %in% medoids),],
#                               train[which(train$y=="Yes"),])

>>>>

```{r}
IR_gm12878_10kb <- numeric(22)

#reading in whole genome data
whole_genome_dat <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/gm12878_10kb.rds")
#reading in bin data on the whole genome that contains chromosome information
binslist_dat <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/binslist10.rds")

for(i in 1:22){
  #reducing the whole genome data to only specific chromosome
	reduce_chr <- paste0("chr", i)
	chr_specific_dat <- whole_genome_dat[which(as.character(seqnames(binslist_dat))==reduce_chr),]

  IR_gm12878_10kb[i] <- length(chr_specific_dat$y[which(chr_specific_dat$y=="Yes")])/length(chr_specific_dat$y[which(chr_specific_dat$y=="No")])
}

@@

```{r}
IR_gm12878_25kb <- numeric(22)

#reading in whole genome data
whole_genome_dat <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/training_testing/gm12878_25kb.rds")
#reading in bin data on the whole genome that contains chromosome information
binslist_dat <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/training_testing/binslist25.rds")

for(i in 1:22){
  #reducing the whole genome data to only specific chromosome
	reduce_chr <- paste0("chr", i)
	chr_specific_dat <- whole_genome_dat[which(as.character(seqnames(binslist_dat))==reduce_chr),]

  IR_gm12878_25kb[i] <- length(chr_specific_dat$y[which(chr_specific_dat$y=="Yes")])/length(chr_specific_dat$y[which(chr_specific_dat$y=="No")])
}

@@

```{r}
IR_gm12878_50kb <- numeric(22)

#reading in whole genome data
whole_genome_dat <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/training_testing/gm12878_50kb.rds")
#reading in bin data on the whole genome that contains chromosome information
binslist_dat <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/training_testing/binslist50.rds")

for(i in 1:22){
  #reducing the whole genome data to only specific chromosome
	reduce_chr <- paste0("chr", i)
	chr_specific_dat <- whole_genome_dat[which(as.character(seqnames(binslist_dat))==reduce_chr),]

  IR_gm12878_50kb[i] <- length(chr_specific_dat$y[which(chr_specific_dat$y=="Yes")])/length(chr_specific_dat$y[which(chr_specific_dat$y=="No")])
}

@@

```{r}
IR_gm12878_100kb <- numeric(22)

#reading in whole genome data
whole_genome_dat <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/training_testing/gm12878_100kb.rds")
#reading in bin data on the whole genome that contains chromosome information
binslist_dat <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/training_testing/binslist100.rds")

for(i in 1:22){
  #reducing the whole genome data to only specific chromosome
	reduce_chr <- paste0("chr", i)
	chr_specific_dat <- whole_genome_dat[which(as.character(seqnames(binslist_dat))==reduce_chr),]

  IR_gm12878_100kb[i] <- length(chr_specific_dat$y[which(chr_specific_dat$y=="Yes")])/length(chr_specific_dat$y[which(chr_specific_dat$y=="No")])
}

@@

```{r}
IR_K562_10kb <- numeric(22)

#reading in whole genome data
whole_genome_dat <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/K562_10kb.rds")
#reading in bin data on the whole genome that contains chromosome information
binslist_dat <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/binslist10.rds")

for(i in 1:22){
  #reducing the whole genome data to only specific chromosome
	reduce_chr <- paste0("chr", i)
	chr_specific_dat <- whole_genome_dat[which(as.character(seqnames(binslist_dat))==reduce_chr),]

  IR_K562_10kb[i] <- length(chr_specific_dat$y[which(chr_specific_dat$y=="Yes")])/length(chr_specific_dat$y[which(chr_specific_dat$y=="No")])
}

@@

```{r}
IR_K562_25kb <- numeric(22)

#reading in whole genome data
whole_genome_dat <- readRDS("Z:/TAD_data_analysis/K562/25kb/training_testing/K562_25kb.rds")
#reading in bin data on the whole genome that contains chromosome information
binslist_dat <- readRDS("Z:/TAD_data_analysis/K562/25kb/training_testing/binslist25.rds")

for(i in 1:22){
  #reducing the whole genome data to only specific chromosome
	reduce_chr <- paste0("chr", i)
	chr_specific_dat <- whole_genome_dat[which(as.character(seqnames(binslist_dat))==reduce_chr),]

  IR_K562_25kb[i] <- length(chr_specific_dat$y[which(chr_specific_dat$y=="Yes")])/length(chr_specific_dat$y[which(chr_specific_dat$y=="No")])
}

@@

```{r}
IR_K562_50kb <- numeric(22)

#reading in whole genome data
whole_genome_dat <- readRDS("Z:/TAD_data_analysis/K562/50kb/training_testing/K562_50kb.rds")
#reading in bin data on the whole genome that contains chromosome information
binslist_dat <- readRDS("Z:/TAD_data_analysis/K562/50kb/training_testing/binslist50.rds")

for(i in 1:22){
  #reducing the whole genome data to only specific chromosome
	reduce_chr <- paste0("chr", i)
	chr_specific_dat <- whole_genome_dat[which(as.character(seqnames(binslist_dat))==reduce_chr),]

  IR_K562_50kb[i] <- length(chr_specific_dat$y[which(chr_specific_dat$y=="Yes")])/length(chr_specific_dat$y[which(chr_specific_dat$y=="No")])
}

@@

```{r}
IR_K562_100kb <- numeric(22)

#reading in whole genome data
whole_genome_dat <- readRDS("Z:/TAD_data_analysis/K562/100kb/training_testing/K562_100kb.rds")
#reading in bin data on the whole genome that contains chromosome information
binslist_dat <- readRDS("Z:/TAD_data_analysis/K562/100kb/training_testing/binslist100.rds")

for(i in 1:22){
  #reducing the whole genome data to only specific chromosome
	reduce_chr <- paste0("chr", i)
	chr_specific_dat <- whole_genome_dat[which(as.character(seqnames(binslist_dat))==reduce_chr),]

  IR_K562_100kb[i] <- length(chr_specific_dat$y[which(chr_specific_dat$y=="Yes")])/length(chr_specific_dat$y[which(chr_specific_dat$y=="No")])
}
